% Lecture Template for ME3050-001-002-Tristan Hill - Spring 2020 - Summer
% Dynamics Modeling and Controls
% Higher Order Systems - Modeul 13 - Topic 2

% I am finally converting my stuff to BEAMER

% Document settings

%\documentclass{beamer}                  % for presentation ?
\documentclass[handout]{beamer}  % for handout ?
\usepackage{beamerthemesplit}
\usepackage{amsmath}
\usepackage{listings}
\usepackage{multicol}
\usepackage{framed}
\usepackage{amsmath, nccmath}
\usepackage{geometry}
\usepackage{bm}

\beamertemplateballitem

\definecolor{TTUpurple}{rgb}{0.3098, 0.1607, 0.5176} % TTU Purple (primary)
\definecolor{TTUgold}{rgb}{1.0000, 0.8666, 0.0000} % TTU Gold (primary)

\setbeamercolor{palette primary}{bg=TTUpurple,fg=TTUgold}
\setbeamercolor{palette secondary}{bg=black,fg=TTUgold}
\setbeamercolor{palette tertiary}{bg=black,fg=TTUpurple}
\setbeamercolor{palette quaternary}{bg=TTUgold,fg=black}
\setbeamercolor{structure}{fg=TTUpurple} % itemize, enumerate, etc
\setbeamercolor{section in toc}{fg=TTUpurple} % TOC sections

%\usefonttheme{professionalfonts}

\newcommand{\Lagr}{\mathcal{L}} % lagrangian

\newcommand{\hspcu}{\underline{\hspace{20mm}}} % large horizontal space w underline
\newcommand{\vspccc}{\vspace{6mm}\\} % large vertical space
\newcommand{\vspcc}{\vspace{4mm}\\}   % medium vertical space
\newcommand{\vspc}{\vspace{2mm}\\}     % small vertical space

\newcommand{\hspcccc}{\hspace{10mm}} % large horizontal space
\newcommand{\hspccc}{\hspace{6mm}} % large horizontal space
\newcommand{\hspcc}{\hspace{4mm}}   % medium horizontal space
\newcommand{\hspc}{\hspace{2mm}}     % small horizontal space

\newsavebox{\mybox} % custom box

\newcommand{\MNUM}{13\hspace{2mm}} % Module number
\newcommand{\TNUM}{2\hspace{2mm}} % Topic number 
\newcommand{\moduletitle}{Higher Order Systems} % Titles and Stuff
\newcommand{\topictitle}{State Space Representations} 

\newcommand{\sectiontitleI}{State Space Models} % More Titles and Stuff
\newcommand{\sectiontitleII}{The State Space Equation}
\newcommand{\sectiontitleIII}{The Output Equation}
\newcommand{\sectiontitleIV}{Simulation and Control}

\author{ME3050 - Dynamics Modeling and Controls}
\title{Module \MNUM - \moduletitle}
\date{Mechanical Engineering\vspc Tennessee Technological University}

\begin{document}

\lstset{language=MATLAB,basicstyle=\ttfamily\small,showstringspaces=false}

\frame{\titlepage \center\begin{framed}\Large \textbf{Topic \TNUM - \topictitle}\end{framed} \vspace{5mm}}

% Section 0 - Outline
\frame{
	
	\large \textbf{Topic \TNUM - \topictitle} \vspace{3mm}\\
	
	\begin{itemize}
	
		\item \sectiontitleI    \vspc % Section I
		\item \sectiontitleII 	\vspc % Section II
		\item \sectiontitleIII 	\vspc %Section III
		\item \sectiontitleIV 	\vspc %Section IV
	
	\end{itemize}

}


\section{\sectiontitleI}

\frame{
  \frametitle{\sectiontitleI}
    \begin{itemize}

		\item {\it commonly used} for system models \\

		\item useful for {\it numerical simulation}\\

		\item used in the area of {\it automatic control}\\

		\item an ODE system has an equivalent State Space Model representation\\

	\end{itemize}  

}


\frame{
  \frametitle{\sectiontitleI}
  
\textbf{ Higher Order Differential Equations} - An $N^{th}$ order differential equation can be decomposed into a system of $N$ first order differential equations. The resulting system is equivalent to the original equation. \vspace{30mm}

}

\section{\sectiontitleII}

\frame{
  \frametitle{\sectiontitleII}
\textbf{  The State Equation} 
	After the system of differential equations consists of first order equations only, these equations form the state equation.  

}

\frame{
  \frametitle{\sectiontitleII}
\textbf{  The State Equation} 

	\[ \bm{ \dot{x} } = \bm{Ax} + \bm{Bu} \]

	\begin{itemize}

		\item there are n {\it state variables} or {\it states} called $x_1 - x_n$ 
		\item there are m {\it inputs} called $u_1 - u_m$ 
		\item the {\it state vector} $\bm{x}$ is a collumn vector with {\it n} rows
		\item the {\it system matrix} $\bm{A}$ is a square matrix {\it n} rows and {\it n} columns.
		\item the {\it input vector} $\bm{u}$ is a column vector with {\it m} rows.
		\item the {\it control or input matrix} $\bm{B}$ is a matrix with {\it n} rows and {\it m} columns. 
	\end{itemize}		
		
}



\section{\sectiontitleIII}

\frame{
  \frametitle{\sectiontitleIII}
\textbf{ The Output Equation} 

	\[ \bm{y } = \bm{Cx} + \bm{Du} \]

	\begin{itemize}

		\item the {\it output vector} $\bm{y}$ is a collumn vector with {\it p} rows
		\item the {\it output matrix} $\bm{C}$ is a square matrix {\it p} rows and {\it n} columns.
		\item the {\it control matrix} $\bm{D}$ is a matrix with {\it p} rows and {\it m} columns.

	\end{itemize}

}


\frame{  
  \frametitle{\sectiontitleIII}
  
  You can choose any combination of dependent variables or derived quantities for the output equation for your individual purposes. \vspc
  
  This makes the state space model very useful to the designer. 

}

\section{\sectiontitleIV}


\frame{  
  \frametitle{\sectiontitleIV}

    \begin{itemize}

		\item {\it commonly used} for system models \\

		\item useful for {\it numerical simulation}\\

		\item used in the area of {\it automatic control}\\

		\item an ODE system has an equivalent State Space Model representation\\

	\end{itemize}


}

% references is not a section for now, for looks and it would be a waste of space
\frame{

\frametitle{References}

\begin{itemize}
	\item System Dynamics, Palm III, Third Edition - Chapter 4 - Spring and Damper Elements in Mechanical Systems - pg. 208
\end{itemize}

}
\end{document}









